---
title       : Ideal Weight Calculator
subtitle    : 
author      : Stas Parshin, 2014
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview

* The ideal human body weight has been a topic of debate for a very long time. Hundreds of formulas and theories have been invented and put to the test, but the answer is still debatable. 

* The major factors that contribute to a person's ideal weight are height, gender, age, body frame, body type, and so on.

* This simple calculator manipulates only gender and height.

---
## Formulas

### Here is a list of the "ideal weight" formulas used in this app:

* __J. D. Robinson Formula (1983)__  
52 kg + 1.9 kg per inch over 5 feet       (man)  
49 kg + 1.7 kg per inch over 5 feet       (woman)

* __G. J. Hamwi Formula (1964)__  
48.0 kg + 2.7 kg per inch over 5 feet       (man)  
45.5 kg + 2.2 kg per inch over 5 feet       (woman)

* __The World Health Organization (WHO) Recommended Healthy BMI Range__  
18.5 - 25 for both man and woman

---
## Examples

### If you're 30-year-old man, 180cm tall  
* Based on the Robinson formula (1983), your ideal weight is __72.6 kgs__
* Based on the Hamwi formula (1964), your ideal weight is __77.3 kgs__
* Based on the healthy BMI recommendation, your recommended weight is __59.9 kgs - 81.0 kgs__

### If you're 30-year-old woman, 170cm tall
* Based on the Robinson formula (1983), your ideal weight is __60.8 kg__s
* Based on the Hamwi formula (1964), your ideal weight is __60.7 kgs__
* Based on the healthy BMI recommendation, your recommended weight is __53.5 kgs - 72.3 kgs__

---
## Interactive Example

### Result of Robinson formula for previous man and woman in code view

```{r echo=FALSE}
cm5feet <- 152.4
cm1inch <- 2.54
minBMI <- 18.5
maxBMI <- 25
```

```{r}
w <- function(height, weight, diff) {
  round(weight + diff * (height-cm5feet)/cm1inch, 1)
}

w1 <- function(sex, height) {
  w <- if(sex==1) 52 else 49
  d <- if(sex==1) 1.9 else 1.7
  w(height, w, d)
}
```

```{r echo=FALSE}
paste(w1(1, 180), "kg", " is your ideal weight based on the Robinson formula (1983)")
paste(w1(2, 170), "kg", " is your ideal weight based on the Robinson formula (1983)")
```